\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-07 k-planar.tex
More figures and updates
Pfffft

@@

	Observe that each of the faces $F_1,\ldots,F_m$ is contained in a single inner face of $M$.   Let $Y^+ := \overline{Y}^+-F$. Therefore, $V(F_i)$ can be partitioned into at most three sets $P_1'$, $P_2'$, and $P_3'$ where $P_1'\subset V(Y^+)$, $P_2'\subseteq P_a$, $P_3'\subseteq P_b$ for some $a,b\in\{1,2,3\}$, and $F_i[P_j']$ is a path, for each $j\in\{1,2,3\}$.

	Finally, the subgraph $N_i$ of $G$ consisting of the edges and vertices of $G$ contained in $F_i$ or its interior does not contain one of the three vertices of $\tau$. Therefore, we can apply induction using the cycle $F_i$ and the partition $P_1',P_2',P_3'$ of $V(C_i)$ to obtain the desired $H$-partition and tree decomposition of $N_i$.

	The proof finishes in the same way as the proof in \cite{DJMMUW20}.  The paths $P_1,\ldots,P_k$, and $S=V(Y^+)$ become elements of the $H$-partition.
	Elements in each of the $H$-partitions of $N_1,\ldots,N_3$ that intersect $P_1,\ldots,P_k$, or $V(\overline{Y}^+-F)$ are discarded and all the resulting sets are combined to obtain an $H$-partition of $G$.  The desired tree decomposition of $G$ is obtained in exactly the same way as in the proof of Lemma~14 in \cite{DJMMUW20}, except that now each node $x$ has a child for each face $F_i$ of $M^+_x$ that contains a vertex of $G$ in its interior.

>>>>

  \begin{figure}
    \begin{center}
      \begin{tabular}{c@{\hspace{1cm}}c}
        \includegraphics{figs/mmplus-1} & \includegraphics{figs/mmplus-2} \\
        $M$ & $M^+$
      \end{tabular}
    \end{center}
    \caption{The graphs $M$ and $M^+$.}
    \label{boring_figure}
  \end{figure}

@@

	Observe that each of the faces $F_1,\ldots,F_m$ is contained in a single inner face of $M$.  Therefore, $V(F_i)$ can be partitioned into at most three sets $P_1'$, $P_2'$, and $P_3'$ where $P_1'\subset V(Y^+)$, $P_2'\subseteq P_a$, $P_3'\subseteq P_b$ for some $a,b\in\{1,2,3\}$, and $F_i[P_j']$ is a path, for each $j\in\{1,2,3\}$.\note{PM}{This latter requirement requires that $M^+$ be $2$-connected, we should mention this.}
  Therefore, we can apply induction using the cycle $F_i$ and the partition $P_1',P_2',P_3'$ of $V(F_i)$ to obtain the desired $H$-partition $\mathcal{P}_i$ and tree decomposition of subgraph $N_i$ of $G$ contained in $F_i$.

	The proof finishes in the same way as the proof in \cite{DJMMUW20}.  The paths $P_1,\ldots,P_k$, and $S=V(Y^+)$ become elements of the $H$-partition.
  Elements in each of the $H$-partitions of $N_1,\ldots,N_m$ that intersect $P_1,\ldots,P_k$, or $V(\overline{Y}^+-F)$ are discarded and all the resulting sets are combined to obtain an $H$-partition of $G$.  The desired tree decomposition of $G$ is obtained in exactly the same way as in the proof of Lemma~14 in \cite{DJMMUW20}.  The root node contains the nodes of $H$ corresponding to $P_1,\ldots,P_k$.  The root has one child that contains the at most $4$ nodes of $H$ corresponding to $P_1,\ldots,P_k$ and $Y^+$.  This root has up to three children, each of which contains $Y^+$ and at most two of $P_1,\ldots,P_k$.  For each $i\in\{1,\ldots,m\}$, the tree decomposition of $N_i/\mathcal{P}_i$ is then attached to one of these three children.
